---
title: "Task 18"
author: "Callan Mix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
pacman::p_load(tidyquant,dygraphs,timetk)

```

```{r load_data}
kroger <- c("KR") %>% 
  tq_get(get = "stock.prices", from = "2014-03-07")
```

## Background

Interactive visualizations can often be powerful for data investigations. They let your team get at questions in real time. Use the Kroger (KR) stock price to build an interactive visualization of their performance over the last five years. Take some time to build a couple of different visualizations that show Krogers performance. See the task items below for a description.

## Data Wrangling

```{r tidy_data}
kr_ts <- tk_xts(kroger, start = "2014-03-07", date_var = date, select = adjusted)
```

## Data Visualization

```{r plot_data}
dygraph(kr_ts) %>% 
  dyRangeSelector() %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = .25, colors = "orange") 

```

```{r }
dygraph(kr_ts) %>% 
  dyRangeSelector() %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = .25, colors = "red") %>% 
  dyRebase(value = 10000)

```

```{r }
dygraph(kr_ts) %>% 
  dyRangeSelector() %>% 
  dyOptions(fillGraph = TRUE, fillAlpha = .25, colors = "blue") %>% 
  dyAnnotation("2017-6-14", text = "Whole Foods and Amazon", attachAtBottom = TRUE, width = 160) 
```


## Conclusions

My choice of graphs follows what Brother Hathaway did in class. They are very good though at displaying the data clearly and helping the user to understand patterns and time. I really enjoy using the interactive graphs and hope to do more with them in the future. 
