---
title: "Task 13"
author: "Callan Mix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}

library(tidyverse)

```

```{r load_data}
dart_csv <- read_csv("https://github.com/byuistats/data/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.csv")


```

## Background

When we are visualizing data with categorical variables, we have to deal with character strings as groupings. The problem with summarizing categorical data in a table or a plot is how to order the groups. Using the concept of Factors allows us to dictate the order of these groupings for presentation. We will revisit the stock data from a previous task to create a table and a plot that has the months correctly labeled and ordered.

## Data Wrangling

```{r tidy_data}

clean_stocks <- dart_csv %>% 
  separate(contest_period, c("month_beg", "year"), sep = "-") %>%  
  separate(year, c("month_end", "year_end"), sep = -4) %>% 
  mutate(month_beg = str_extract(month_beg,".*[:alpha:]"), 
         month_end = case_when(month_end == "Dec." ~ "December",
                              month_end == "Febuary" ~ "February",
                              TRUE ~ month_end)) 
head(clean_stocks)
```

## Data Visualization

```{r plot_data}

clean_stocks %>% 
  mutate(month_end = factor(month_end,month.name)) %>% 
  ggplot(aes(x = month_end, y = value)) +
  geom_violin(aes(group = month_end, fill = month_end), show.legend = FALSE) +
  labs(x = "Months", y = "Values")

```

This shows the six month returns for each of these months. 

```{r }
clean_stocks %>% 
  mutate(month_end = factor(month_end,month.name)) %>% 
  ggplot(aes(x = month_end, y = value)) +
  geom_violin(aes(group = month_end, fill = month_end), show.legend = FALSE) +
  labs(x = "Months", y = "Values") +
  facet_wrap(facets = "variable") 
  

```

And this one shows the data from each of the stocks. 