---
title: "Case Study Number 1"
author: "Callan Mix"
date: "`2019-01-11`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)

```

[Game of Thrones Dialogue Visualization](http://beta.wind-and-words.com/seasons/1/dialogue)

#This is a really cool code that shows how much a charactor talked and to whom they talked.
#The movement and navagation are seemless and the whole thing just looks nice.
#One problem is that it can take a few seconds to udnerstand what is going on and what the point is.


[Apollo Missions](https://www.madefromdata.com/product/apollo-black)

#This shows all of the Apollo missions and where they went. It is amzaing to see how each mission is shown in comparison to the others and also shows major events from each mission.
#It is easy to follow and find the mission that you are looking for. 
#One downside to this graphic would be its lack of an interactive function to make locating individual missions an easier task.

[Artificial Intelegence](https://priceonomics.com/which-industries-are-investing-in-artificial/)


#This is a page of graphics that explain the trend of investing into artificial intelegence by major company recently. None of the graphs are super exciting, but that is the point, to clearly communicate the data to the user without any room for error. This lets me know what the point is within seconds of seeing the graphs. 
#One down side is that the graphs are to be used with the artical and not much without.

[China VS US Steel Production](https://www.washingtonpost.com/business/2019/01/09/chinas-slowdown-is-biggest-threat-world-economy/?utm_term=.79dded46f829)


#This is the most simple graph I have researched and I wanted to include it because it is within my range of abilities to produce. 
#I like that it is simplistic and that you can get the point of the graph within moments of seeing it. It is clear in that regard. 
#One thing that I might have changed would have been to add some more of labels.


```{r}
plot(1:20)
```